Geographical Python Teaching Resources: GeoPyTeR

### 2019-10-15 Geopyter.tex
Refs

Regardless of whether this is a revolution \citep{Wyly2014,Torrens2010} or an
evolution \citep{Barnes2013,Barnes2014,ArribasBel2018}, there is no question
that teaching students and researchers how to code and how to \textit{think}
computationally presents new challenges \citep{Etherington2016,Muller2014}.
Specifically, because of the way that these changes have unfurled, the majority
of resources used in the classroom are being developed from scratch at each
institution, and often by newly-appointed lecturers and assistant professors
coming from the relatively small number of elite research facilities active in
this domain (see discussion in \citealp{esrc2013}). Not only has this led to the
duplication of effort at multiple sites, but it has also had an enormous impact
on the productivity---as commonly measured by institutions---of early career
researchers, many of whom are in their first teaching post.

@@

We drew inspiration from the \textsc{foss} iPython project
\citep{perez_2007_ipython} and its transformative impact on the sharing of
integrated code, text, and multimedia resources. And we also looked to the
Python Spatial Analysis Library (\textsc{p}y\textsc{sal}) project in which
contributors take ownership of application areas through managed collaboration
instead of a contributory `free-for-all'. The subsequent emergence of the
Jupyter project \cite{kluyver16} from iPython has led to the rapid growth of a
rich ecosystem of tools that support the kinds of interaction needed to make
this an effective teaching resource: multiuser-notebooks (jupyterhub),
automation of grading (nbgrader), interactive widgets for visualisation
(ipywidgets), and packages to facilitate manipulation of the notebook itself
(nbformat and notebook).

>>>>

Regardless of whether this is a revolution \citep{Wyly2014,Torrens2010} or an
evolution \citep{Barnes2013,Barnes2014,ArribasBel2018}, there is no question
that teaching students and researchers how to code and how to \textit{think}
computationally presents new challenges
\citep{Etherington2016,Muller2014,rey_09jgs}. Specifically, because of the way
that these changes have unfurled, the majority of resources used in the
classroom are being developed from scratch at each institution, and often by
newly-appointed lecturers and assistant professors coming from the relatively
small number of elite research facilities active in this domain (see discussion
in \citealp{esrc2013}). Not only has this led to the duplication of effort at
multiple sites, but it has also had an enormous impact on the productivity---as
commonly measured by institutions---of early career researchers, many of whom
are in their first teaching post.

@@

We drew inspiration from the \textsc{foss} iPython project
\citep{perez_2007_ipython} and its transformative impact on the sharing of
integrated code, text, and multimedia resources. And we also looked to the
Python Spatial Analysis Library (\textsc{p}y\textsc{sal}) project
\cite{rey_19sea}in which contributors take ownership of application areas
through managed collaboration instead of a contributory `free-for-all'. The
subsequent emergence of the Jupyter project \cite{kluyver16} from iPython has
led to the rapid growth of a rich ecosystem of tools that support the kinds of
interaction needed to make this an effective teaching resource:
multiuser-notebooks (jupyterhub), automation of grading (nbgrader), interactive
widgets for visualisation (ipywidgets), and packages to facilitate manipulation
of the notebook itself (nbformat and notebook).
